Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-06 papers/paper_review/response_1.txt

REVIEWER COMMENT
----------
Figure 4, H-alpha plot:
- Only the part of the plot showing M0 and earlier is really useful here, perhaps limit the axis range.
- It is difficult to distinguish the field stars and TucHor stars in black and white
- There must be more field K stars with H-a measurements for comparison; the two showing in the late K dwarf regime don't do a good job of illustrating how H-a inactive field K dwarfs are. It can be inferred from Rauscher & Marcy (2006), although I couldn't really find an appropriate reference for field K dwarfs since 1990 (https://iopscience.iop.org/article/10.1086/132624). However, https://academic.oup.com/mnras/article/476/1/908/4828379#112872390 includes hotter stars in numerous clusters.

RESPONSE
----------
> - We have limited the axis range.
>
> - We have updated the markers to be more distinguishable.
>
> - Good point regarding the field comparison.  We have replaced it for the Pleaides using the data from Fang+2018, as suggested.

@@

REVIEWER COMMENT
----------
The discussion of centroid offsets could use further elaboration.
- Line 664: how many sigma is 0.4"? Is this generally considered a good value?
- 1643 and 7368 both have centroid shifts that are larger than normal for Kepler, and it is stated that stellar variability is the likely cause. But not all young stars show centroid shifts, and presumably some level of centroid shift would still be concerning. Is the impact of stellar variability well established in the literature? Can the amplitude of stellar variability be used to inform one about the centroid offsets?
- The discussion for 7368 indicates that the centroid shift can't be due to another star due to the high contrast imaging constraints. Is there an established method for this? Can the same analysis be done for 1643?

RESPONSE
----------
> The Data Validation Summaries for the KOIs are available at the following links, for reference.
> Kepler-1643: https://exoplanetarchive.ipac.caltech.edu/data/KeplerData/008/008653/008653134/dv/kplr008653134-001-20160209194854_dvs.pdf
> KOI-7368: https://exoplanetarchive.ipac.caltech.edu/data/KeplerData/010/010736/010736489/dv/kplr010736489-001-20160209194854_dvs.pdf
> KOI-7913: https://exoplanetarchive.ipac.caltech.edu/data/KeplerData/008/008873/008873450/dv/kplr008873450-006-20160209194854_dvs.pdf
>
> - Re: 0.4" and "good values", \citet{bryson_2013} showed that for typical field star KOIs without centroid offsets, the mean offset distribution peaks at 0.3$''$ (their Figure 23).  By comparison, stars with centroid offsets that can be localized to nearby stars have a distribution that peaks at 7$''$ (their Figure 32).  The stellar variability in Kepler-1643 complicates the centroid-based vetting tests, because the shifts measured by these tests are determined from the in- and out-of-transit flux-weighted centroids.  For stars with significant spot-induced variability there is no static baseline in either the in- or out-of-transit , and so the centroid location may shift depending on the rotational phase combined with the local scene.  Nonetheless, it appears that the centroid-level diagnostics for Kepler-1643 are consistent with the transit signal being localized to the target star, though only at moderate confidence.  We have modified the text to include these points.
>
> - Re: what level of centroid shift is concerning -- if the centroid shifts across quarters were consistently >~ 1 arcsecond (and measured at ~0.1 arcsecond precision), and in the same direction across many Kepler quarters, it would be much more concerning.  However the outlier centroid shifts in Kepler-1643 and KOI-7368 appear to be in effectively random directions, which suggests that the stellar rotation and systematic errors in the NASA SPOC pipeline's whitening are more likely to be the root cause.  A few sentences have been modified to this effect.
>
> - Re: methods for establishing whether other stars can create the centroid shift, and Kepler-1643, yes, the same logic applies.  We have added a comment to the manuscript to this effect.  The "established method" for this is the logic laid out by Bryson+2013.  For instance, given the target star T and a neighbor star N separated by distance D, one can calculate the expected centroid shifts for the various scenarios where the target T hosts an eclipse signal of depth δ, and also when the neighbor N hosts the signal.  We do not present these calculations in the text, because there is no evidence that the offset itself is statistically signficant.  Nonetheless, the absence of companions for Kepler-1643 and KOI-7368 does help bolster the interpretation.

### 2022-09-06 papers/paper/ms.tex
update response

Intriguingly, Kepler-1643 failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset --- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$.
This is an instructive exercise in how stellar
variability complicates centroid-based vetting tests.  The 
shifts measured by these tests are determined from the in- and
out-of-transit flux-weighted centroids.  For stars with significant
spot-induced variability there is no static baseline in either the in-
or out-of-transit phases.

@@

It bears mentioning that KOI-7368 shows a centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  Since the remaining data show
consistent scatter in their centroid locations, these
outlying quarters are likely also caused by the stellar variability.  
Our NIRC2 imaging independently shows that there are no neighboring
sources that could cause an offset of the observed amplitude.

>>>>

Intriguingly, Kepler-1643 failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's \added{KIC }catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset --- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$\added{ (3-$\sigma$)}.
\added{\citet{bryson_2013} showed that for typical field star KOIs without
centroid offsets, the mean offset distribution peaks at 0.3$''$ (their
Figure 23).  By comparison, stars with centroid offsets that can be
localized to nearby stars have a distribution that peaks at 7$''$ (their
Figure 32). } \replaced{This is an instructive exercise in how }{The }stellar
variability \added{in Kepler-1643} complicates \added{the} centroid-based
vetting tests\replaced{. The}{, because the} shifts measured by these tests are
determined from the in- and out-of-transit flux-weighted centroids.  For stars
with significant spot-induced variability there is no static baseline in either
the in- or out-of-transit phases\added{, and so the centroid location may shift
depending on the combination of the rotation phase combined and the local scene.  Based on
these considerations, the centroid-level diagnostics for Kepler-1643 appear to
be consistent with the transit signal being localized to the target star}.

@@

It bears mentioning that KOI-7368 shows a centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
\added{formally }significant ($0\farcs2$; 3.0-$\sigma$).  Again, the
data validation reports show that the shift is caused by a few
outlying quarters (4, 5, 8, and 12).  Since the remaining data show
consistent scatter in their centroid locations, these outlying
quarters are likely also caused by the stellar variability\added{,
since their directions across different quarters are inconsistent}.
Our NIRC2 imaging independently shows that there are no \added{known
}neighboring sources that could cause an offset of the observed
amplitude\added{, as is also the case for Kepler-1643}.
